A Rapid Feasibility Checking for Reconfiguration of Mismatched PV Arrays

### 2019-05-03 PVSC-46/Manuscript/PVSC_Manuscript.tex
compliar on arch
Updates from Overleaf
Finish the first version 2019/05/04

\begin{abstract}
%\boldmath
Power generation efficiency of photovoltaic (PV) arrays is significantly affected by partial shading and PV cell damage. Partial shading or PV cell damage induces mismatched power generation among PV panels and causes an efficiency loss of power generation. Power generation of mismatched PV arrays can be recovered by reconfiguring connection of PV panels. 
In this paper, we introduce a \textit{feasibility check problem} of PV panel configuration.
The problem identifies whether a connection among PV panels can be configured from a given PV module level solution. 
We also propose an algorithm for the feasibility check problem. The experimental results demonstrate that the proposed method can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors. 
\end{abstract}

@@

\section{Introduction}
As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
However, due to the nature of a PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
PV cells could not uniformly generate power when PV cells experience different irradiances or some of cells have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging. 
To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
However, it causes a significant loss of power generation.

PV arrays are hierarchically constructed such that a group of PV cells form a PV module, a group of PV modules form a PV panel, and a group of PV panels form a PV array. 
Power generation of mismatched PV arrays can be recovered by reconfiguring connection of these components. 
Fig.\ref{compare} shows an example of power generations of a PV array with a partial shading. 
We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
Before reconfiguration, it has four peaks in power VS voltage curve, while,  if we reconfigure connection among PV panels, it can increase around 35\% power generation.

Though several reconfiguration methods have been proposed, most works consider reconfiguration in PV cell or PV module level \cite{nguyen2008adaptive,wang2014architecture,storey2013improved,storey2014optimized,udenze2018reconfiguration}. 
However, cell level reconfiguration requires a significantly high computation time and a large number of switches for reconfiguration. 
In addition, they require a special PV panels with capability of switching, and cannot be applied to the system constructed with standard PV panels. 
From a practical view, reconfiguration of connection among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected. 
\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{PVSC-46/fig/compare.png}
    \caption{Power generation before and after reconfiguration}
    \label{compare}
\end{figure}

Reconfiguration in PV panel level has been investigated\cite{carotenuto2015evolutionary,hu2017non,orozco2016optimized}. 
A PV array reconfiguration using genetic algorithm (GA) was proposed in \cite{carotenuto2015evolutionary}. Though it can give a new configuration, computing cost is significantly high and the algorithm cannot generate the best configuration precisely.  
Hu et al. also addressed PV panel reconfiguration where they formulate a nonlinear integer programming problem to optimize power generation by reconfiguration \cite{hu2017non}.
Orozco-Gutierrez et al. proposed an efficient and effective reconfiguration method\cite{orozco2016optimized} where it first selects candidates of configurations with approximation and then finds the best one with precise power simulation. 
However, the candidates are specified in a PV module level though PV modules could not be fully reconfigured. Actually, we found that some of configuration candidates are not able to be realized. However, the paper\cite{orozco2016optimized}  does not show any systematic way to identify such a feasibility.

In this paper, we propose an algorithm to rapidly check feasibility that a given configuration candidate is actually formed by given PV panels. 
The proposed method can efficiently check the feasibility while identifying most feasible cases accurately. 
The experimental results demonstrate the effectiveness of the proposed method can identify the feasibility of configurations and false negative are less than 1\%.

@@

Figure \ref{model} shows an example of a PV array. 
A PV array is a parallel connection of (PV) strings where a string is a series connection of PV panels. 
A PV panel is a series connection of PV modules, and a PV module is a parallel connection of a series of PV cells and a bypass diode. 
A typical PV panel is composed of three PV modules each of which has 12-24 PV cells. 
A PV module can generate power for a given voltage according to its I-V characteristics as shown in Fig.\ref{fig:IV}(a - c). 
The I-V characteristics is affected by irradiance level and physical damage of PV cells. 
Figure \ref{fig:IV}(a) also shows a typical degradation of a I-V characteristics where generated current is reduced with some ratio while keeping the voltage range. 
When a PV panel has a partial shade, that is its PV modules have different irradiance levels and hence different I-V characteristics, the PV panels might have multiple peaks (maximum power points, MPPs) in power generation as shown in Fig.\ref{fig:IV}(d).

To find out accurate I-V characteristics of a PV panel, we need a time consuming power simulation. 
However, we can roughly understand I-V characteristics of a PV panel (and also a string) as follows. 
When a control voltage is low, PV modules with high irradiance level are active while PV modules with low irradiance level are inactive with turning on their bypass diodes.
In this case, a high current can flow in the PV panel. When control voltage is high, some of bypass diodes become turning off and the corresponding PV modules become active. 
In this case, the current level is reduced and generated power sometimes increases and sometimes decreases. 
The generated power at MPPs can be roughly estimated. 
In Fig.\ref{fig:IV}(d), one PV panel has three PV modules with different irradiance levels. 
The peak currents for these modules are 433mA, 307mA, and 155mA, respectively. 
Voltages at MPPs are roughly 200V, 400V, 600V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 200V in this case). 
At the first MPP (MPP1), only one PV module with a peak current of 433mA is active at a control voltage of 206V, so the generated power is 89W. 
At the second MPP (MPP2), two PV modules with peak currents of 433mA and 307mA are active at a control voltage of 420V. 
In this case, the current level of the PV panel is 307mA since two PV panels are connected in series and they have to have the same current level, and the generated power is 129W. At the third MPP (MPP3), the current level of the PV panel is 155mA at a control voltage of 644V, and the generated power is 100W.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{module.png}
    \caption{PV array, string, module and panel}
    \label{model}
\end{figure}

\begin{figure}
     \centering
    \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{PVSC-46/fig/m_1.png}
        \caption{PV module 1}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{PVSC-46/fig/m_2.png}
        \caption{PV module 2}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{PVSC-46/fig/m_3.png}
        \caption{PV module 3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\linewidth}
        \centering
        \vspace{3mm}
        \includegraphics[width=\linewidth]{PVSC-46/fig/panel.png}
        \caption{PV panel}
    \end{subfigure}
    \caption{I-V characteristics}
    \label{fig:IV}
\end{figure}

\section{Orozco-Guierrez's method}\label{Sec3}
In this section, we briefly introduce a method proposed by Orozco-Guierrez et al.\cite{orozco2016optimized} as the most related work to this paper.
Orozco-Guierrez et al. proposed an efficient reconfiguration algorithm for mismatched PV arrays. 
The method utilizes information of MPPs of every PV panel that are extracted using an online monitoring \cite{carotenuto2014online} and a power estimation \cite{orozco2015fast}. 
Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
Table \ref{tab:modules} shows the maximum number of active modules for each current level.

Then power values are approximated for possible configurations. 
Table \ref{tab:powers} shows an example to form a PV array with two strings where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V). 
The method has a simple feasibility check as follows. 
\newline{}
\textbf{(Feasibility 1)} For the $n$-th highest current level $I_{n}$, the number of active modules in a system is $N(I_{n}) / n$ or less. 
\newline{}
Where, $N(I)$ denotes the total number of active modules for a current level $I$. 
For example, consider a candidate current pair (3A. 2.5A). In this case, the highest and the second highest current levels are 3A and 2.5A, respectively, and the total number of active modules for 3A and 2.5A are 3 and 6, respectively (see Table \ref{tab:modules}). Therefore, the number of active modules in the first string is 3 or less, and the number of active modules in the second string is also $ 6/2  = 3$ or less. Consequently, the number of active modules per string is at most 3 for a candidate current pair (3A. 2.5A). Table \ref{tab:powers} has values in the cells when Feasibility 1 is satisfied.

@@

\section{Feasibility}
In the method\cite{orozco2016optimized}, to execute a power simulation for a PV array, we need to assign panels into strings to realize a candidate configuration. 
For example, a candidate configuration for a current pair (2.5A, 2.5A) with 3 active modules is realized by assign panel P2  to the first string and panels P1 and P4 to the second string as shown in Fig.\ref{fig:feasible-configuration}. 
However, we could not find feasible assignment for a current pair (3A, 2.5A) with 3 active modules or a current pair (2.5A, 1.5A) with 4 active modules though they are expected to generate higher powers 330W or 320W. 
That is, the condition Feasibility 1 is a necessary but not sufficient to check the actual feasibility.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{PVSC-46/fig/feasible-configuration.pdf}
    \caption{Feasible configuration}
    \label{fig:feasible-configuration}
\end{figure}

@@

\textit{Definition 1} (\textit{Feasibility Problem}):\\
Input: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
Output: Whether $Q$ with $m$ modules is feasible or not.

\subsection{Outline of the algorithm}
In the proposed algorithm, we try to configure a PV array and identify the feasibility. 
For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s}) (Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$. 
When selecting a panel to a string, we will consider how much we lose an opportunity that the panel is more effectively used for other current level. 
For example, if we select Panel 1 in Table \ref{tab:modules} for a string with a current level 3A, two modules can be active while the remaining one module becomes inactive. 
The remaining one module still is not active if $P1$ is used for a current level 2,5A, while it can be active if it is used for current level 1.5A or 0.5A. 
We will consider that when selecting $P1$ for a current level 3A, we don't have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
The algorithm select panels so as to minimize such losses.

@@

\subsection{Algorithm}
Step 1 sorts unselected panels (with modules that can be active for the target current), and Step 2 selects panels one by one in the sorted order until reaching the required number of active modules.

Step 3 optimizes the number of active modules. 
In Step 3, if the number of active modules exceeds the required number $m$, redundant panels are canceled if exist. 
A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
Redundant panels are searched at loss level. 
Starting with a loss level where the last panel is selected, we will check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
where $Q_{n}$ is a required current level for the current string.
Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
If there still exceed $m$ after canceling, we will go to the previous loss level and try to cancel panels.
This procedure is repeated until selecting an exact $m$ active modules or checking all the loss levels.

Step 4 optimizes the number of selected panels.
In Step 4, we will swap selected panels and an unselected panel in the same loss level to reduce the number of selected panels.
There are 3 swap cases as shown in Table \ref{tab:swap}. Algorithm 1 shows a pseudo code of the proposed algorithm.

\begin{table}[t]
\caption{Swap rule}
\label{tab:swap}
\centering
\begin{tabular}{c|c}
\hline\hline
\multicolumn{2}{c}{The numbers of active modules} \\
selected panels & unselected panels \\ \hline
1, 1, 1 & 3 \\ \hline
1, 1 & 2 \\ \hline
1, 2 & 3 \\ \hline
\end{tabular}
\end{table}

\begin{algorithm}
\caption{Feasibility Check}
\LinesNumbered
\SetKwInOut{Input}{Input}  
\Input{
  \textit{$Q = Q_1, Q_2, \ldots , Q_s$}: required current for each string; 
  \textit{$m$}: The minimum number of active modules per string;
  \textit{$M_{p}$}: The number of active modules in each panel \textit{p};
  %\textit{P}: Number of panels; 
  \textit{s}: Number of strings;}
\SetKwInOut{Output}{Output}
\Output{Feasibility Result;%\\
        %Conf: Configuration Result;
        }
\For{\textup{each string} $ k (2 \leq k \leq s)$ \textup{and panel} $p$}{$Loss(p,k) = M_{p}(Q_{k}) - M_{p}(Q_{k-1})$}
\For{j = 1 to s}
    {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panes} $< m$}
       {\textup{\textbf{return :}} Feasibility = NO}}
     $PS$ = a set of unselected panels with $M_{p}(Q_{j}) > 0$;\\
     // step 1\\
     sort $PS$ in a lexicographically ascending order of $Loss(p,j+1)$, $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
     // step 2\\
     select panels in the order in $PS$ until $\sum M_{p}(Q_{j})$ for selected panels $\geq m$;\\
     //step 3\\
     group selected panels $LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$ with loss level ($LV_{1}$ is the lowest level);\\
     \For{i = h to 1}
     {find and cancel redundant panels in $LV_{i}$ in the order in $PS$}
     //step 4\\
     \For{i = h to 1}
     {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
    }
    \textup{\textbf{return :}} Feasibility = YES
\end{algorithm}

\subsection{Evaluation}
Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same

To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV array. For each PV array, contains 6 - 24 PV panels connected into 3 - 6 PV strings. For each PV panel, it will has 3 - 8 working current values.

The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}. As shown in Table \ref{result_compare}, proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.

@@

\begin{table}[t]
\caption{PV Cell Parameters}
\begin{center}
\begin{tabular}{c|c}
\hline \hline
Parameter             & Value  \\ \hline
Short-Circuit Current & 0.66A  \\
MPP-Current           & 0.58A  \\
Open-Circuit Voltage  & 280V   \\
MPP-Voltage           & 215V  \\
Max Power Output      & 124.7W 
\end{tabular}
\end{center}
\label{PV_cell_par}
\end{table}

>>>>

\begin{abstract}
%\boldmath
  Power generation efficiency of photovoltaic (PV) arrays is significantly affected by partial shading and PV cell damage.
  Partial shading or PV cell damage induces mismatched power generation among PV panels and causes an efficiency loss of power generation.
  Power losses of mismatched PV arrays can be recovered by reconfiguring connection of PV panels.
  In this paper, we introduce a \textit{feasibility check problem} of PV panel configuration.
  This problem identifies whether a connection among PV panels can be configured from a given PV module level solution.
  We also propose an algorithm for the \textit{feasibility check problem}.
  The experimental results demonstrate that the proposed algorithm can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors. 
\end{abstract}

@@

\section{Introduction}
As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
However, due to the nature of PV cell, which is a basic component of a PV array.
PV arrays are sensitive to partial shading and PV cell damage. 
PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging. 
To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, it will also introduce voltage drop which cause PV system generates multi maximum power points.
% However, it causes a significant loss of power generation.

PV arrays are hierarchically constructed such that a group of PV cells form a PV module, a group of PV modules form a PV panel, and a group of PV panels form a PV array. 
Power generation of mismatched PV arrays can be recovered by reconfiguring connection of these components. 
Fig.\ref{compare} shows an example of power generations of a PV array with a partial shading. 
We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
Before reconfiguration, it has four peaks in power VS voltage curve, while, after we reconfigured connection among PV panels, power generation increased by 35\%.

Though several reconfiguration methods have been proposed, most works consider reconfiguration in PV cell or PV module level \cite{nguyen2008adaptive,wang2014architecture,storey2013improved,storey2014optimized,udenze2018reconfiguration}. 
However, cell level reconfiguration requires a significantly high computation time and a large number of switches for reconfiguration. 
In addition, they require a special PV panels with capability of switching, and cannot be applied to the system constructed with standard PV panels. 
From a practical view, reconfiguration of connection among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected. 
\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{../fig/compare.png}
    \caption{Power generation before and after reconfiguration}
    \label{compare}
\end{figure}

Reconfiguration in PV panel level has been investigated\cite{carotenuto2015evolutionary,hu2017non,orozco2016optimized}. 
A PV array reconfiguration using genetic algorithm (GA) was proposed in \cite{carotenuto2015evolutionary}. Though it can give a new configuration, computing cost is significantly high and the algorithm cannot generate the best configuration precisely.  
Hu et al. also addressed PV panel reconfiguration where they formulate a nonlinear integer programming problem to optimize power generation by reconfiguration \cite{hu2017non}.
Orozco-Gutierrez et al. proposed an efficient and effective reconfiguration method\cite{orozco2016optimized} where it first selects candidates of configurations using the product of approximated currents and voltages,
then finds the best one with precise power simulation. 
However, these candidates are specified in a PV module level though PV modules could not be fully reconfigured. Actually, we found that some of configuration candidates are not able to be realized. However, the paper\cite{orozco2016optimized}  does not show any systematic way to identify such a feasibility.

In this paper, we propose an algorithm to rapidly check feasibility that a given configuration candidate is actually able to form by given PV panels. 
The proposed method can efficiently check the feasibility while identifying most feasible cases accurately. 
The experimental results demonstrate the effectiveness of the proposed method can identify the feasibility of configurations and false negative are less than 1\%.

@@

Figure \ref{model} shows an example of a PV array. 
A PV array is a parallel connection of (PV) strings where a string is a series connection of PV panels. 
A PV panel is a series connection of PV modules, and a PV module is a parallel connection of a series of PV cells and a bypass diode. 
A typical commerical PV panel is composed of three PV modules each of which has 12-24 PV cells. 
A PV module can generate power for a given voltage according to its I-V characteristics as shown in Fig.\ref{fig:IV}(a - c). 
The I-V characteristics is affected by irradiance level and physical damage of PV cells. 
Figure \ref{fig:IV}(a) also shows a typical degradation of a I-V characteristics where generated current is reduced with some ratio while keeping the voltage range. 
When a PV panel has a partial shade, that is its PV modules have different irradiance levels and hence different I-V characteristics, the PV panels might have multiple peaks (maximum power points, MPPs) in power generation as shown in Fig.\ref{fig:IV}(d).

To find out accurate I-V characteristics of a PV panel, we need to apply a time consuming power simulation. 
However, we can roughly understand I-V characteristics of a PV panel (and also a string) as follows. 
When a control voltage is low, PV modules with high irradiance level are active while PV modules with low irradiance level are inactive with turning on their bypass diodes.
In this case, a high current can flow in the PV panel. When control voltage is increaseing, some of bypass diodes become turning off and the corresponding PV modules become active. 
In that case, the current flow in the panel is determined by current of module with lowest irradiance level, and generated power sometimes increases and sometimes decreases.
% the current level is reduced and generated power sometimes increases and sometimes decreases. 
The generated power at MPPs can be roughly estimated. 
In Fig.\ref{fig:IV}(d), one PV panel has three PV modules with different irradiance levels. 
The peak currents for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
Voltages at MPPs are roughly 22V, 44V, 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
At the first MPP (MPP1), only one PV module with a peak current of 4.5A is active at a control voltage of 22V, so the generated power is 94.6W. 
At the second MPP (MPP2), two PV modules with peak currents of 4.3A and 3.0A are active at a control voltage of 44V. 
In this case, the current level of the PV panel is 3.0A since two PV panels are connected in series and they have to have the same current level, and the generated power is 132W.
At the third MPP (MPP3), the current level of the PV panel is 1.5A at a control voltage of 66V, and the generated power is 99W.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{../fig/module.png}
    \caption{PV array, string, module and panel}
    \label{model}
\end{figure}

\begin{figure}
     \centering
    \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_1.png}
        \caption{PV module 1}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_2.png}
        \caption{PV module 2}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{../fig/m_3.png}
        \caption{PV module 3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\linewidth}
        \centering
        \vspace{3mm}
        \includegraphics[width=\linewidth]{../fig/panel.png}
        \caption{PV panel}
    \end{subfigure}
    \caption{I-V characteristics}
    \label{fig:IV}
\end{figure}

\section{Orozco-Guierrez's method}\label{Sec3}
In this section, we briefly introduce a method proposed by Orozco-Guierrez et al.\cite{orozco2016optimized} as the most related work to this paper.
Orozco-Guierrez et al. proposed an efficient reconfiguration algorithm for mismatched PV arrays. 
The method utilizes information of MPPs of every PV panel that are extracted using an online monitoring \cite{carotenuto2014online} and a power estimation \cite{orozco2015fast}.

For the method in \cite{orozco2016optimized}, first, close values will be approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
Then possible combinations of reconfiguration are enumerated.
For each configuration candidates their generate power value are estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
Table \ref{tab:modules} shows the maximum number of active modules for each current level.
Control voltage for one PV model are approximated to 20V.
Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
% Then power values are approximated for possible configurations. 
Table \ref{tab:powers} shows an example to form a PV array with two strings
where power value is simply multiply PV array current with control voltage for a module and number of active modules per string.
% where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V). 
The method has a simple feasibility check as follows. 
\newline{}
\textbf{(Feasibility 1)} For the $n$-th highest current level $I_{n}$, the number of active modules in a system is $N(I_{n}) / n$ or less. 
\newline{}
Where, $N(I)$ denotes the total number of active modules for a current level $I$. 
For example, consider a candidate current pair (3A. 2.5A). In this case, the highest and the second highest current levels are 3A and 2.5A, respectively, and the total number of active modules for 3A and 2.5A are 3 and 6, respectively (see Table \ref{tab:modules}). Therefore, the number of active modules in the first string is 3 or less, and the number of active modules in the second string is also $ 6/2  = 3$ or less. Consequently, the number of active modules per string is at most 3 for a candidate current pair (3A. 2.5A). Table \ref{tab:powers} has values in the cells when Feasibility 1 is satisfied.

@@

\section{Feasibility}
In the method\cite{orozco2016optimized}, to execute a power simulation for a PV array, we need to assign panels into strings to realize a candidate configuration. 
For example, a candidate configuration for a current pair (2.5A, 2.5A) with 3 active modules is realized by assign panel P2  to the first string and panels P1 and P4 to the second string as shown in Fig.\ref{fig:feasible-configuration}. 
However, we could not find feasible assignment for a current pair (3A, 2.5A) with 3 active modules or a current pair (2.5A, 1.5A) with 4 active modules though they are expected to generate higher powers 330W or 320W. 
That is, the condition Feasibility 1 is a necessary but not sufficient to give a actual feasibility result.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\linewidth]{../fig/feasible-configuration-vertical.pdf}
    \caption{Feasible configuration}
    \label{fig:feasible-configuration}
\end{figure}

@@

\textit{Definition 1} (\textit{Feasibility Problem}):\\
\textbf{Input}: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
\newline
\textbf{Output}: Whether $Q$ with $m$ modules is feasible or not.

\subsection{Outline of the algorithm}
In the proposed algorithm, we try to configure a PV array and identify the feasibility of configuration.
For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s}) (Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$. 
When selecting a panel to a string, we will consider how much we lose an opportunity that the panel is more effectively used for other current level. 
For example, if we select Panel 1 in Table \ref{tab:modules} for a string with a current level 3A, two modules can be active while the remaining one module becomes inactive. 
The remaining one module still is not active if $P1$ is used for a current level 2,5A, while it can be active if it is used for current level 1.5A or 0.5A. 
We will consider that when selecting $P1$ for a current level 3A, we don't have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
The algorithm select panels so as to minimize such losses.

@@

\subsection{Algorithm}
This algorithm roughly divided into 4 steps.

Step 1, sort unselected panels in a lexicographically ascending order of index \textit{Loss} and $M_{P}(Q_{n})$.
This sorting step will give a basic selecting priority for all unselected panels. A panel with uniformly irradiance distribution is perferred over non-uniformly irradiance distributed panel.

Step 2, select panels one by one in the sorted order until reaching the required number of active modules.
In this selection step, panel with no active modules by high selecting priority will be jumped.
That will cut the computational space in the step 3 and step 4.
% Step 1 sorts unselected panels (with modules that can be active for the target current), and Step 2 selects panels one by one in the sorted order until reaching the required number of active modules.

Step 3 optimizes the number of active modules. 
In Step 3, if the number of active modules exceeds the required number $m$, redundant panels are canceled if exist. 
A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
Redundant panels are searched at loss level. 
Starting with a loss level where the last panel is selected, we will check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
where $Q_{n}$ is a required current level for the current string.
Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
If there still exceed $m$ after canceling,
the same cancel panels procedure will operate on previous loss level.
% we will go to the previous loss level and try to cancel panels.
This procedure will repeate until selecting an exact $m$ active modules or checking all the loss levels.

Step 4 optimizes the number of selected panels.
In Step 4, we will swap selected panels and an unselected panel in the same loss level to reduce the number of selected panels.
There are 3 swap cases as shown in Table \ref{tab:swap}.
The swap will keep or minimum total module losses and further reduce the number of panels.
% Pseudo codes are given below to give details to summarize the process of proposed algorithm.
\textbf{\textit{Algorithm 1}} shows a pseudo code of the proposed algorithm.

\begin{table}[ht]
\caption{Swap rule}
\label{tab:swap}
\centering
\begin{tabular}{c|c}
\hline\hline
\multicolumn{2}{c}{The numbers of active modules} \\
selected panels & unselected panels \\ \hline
1, 1, 1 & 3 \\ \hline
1, 1 & 2 \\ \hline
1, 2 & 3 \\ \hline
\end{tabular}
\end{table}

\begin{algorithm}
\caption{Feasibility Check Problem}
\LinesNumbered
\SetKwInOut{Input}{Input}  
\Input{
  \textit{$Q = Q_1, Q_2, \ldots , Q_s$}: required current for each string; 
  \textit{$m$}: The minimum number of active modules per string;
  \textit{$M_{p}$}: The number of active modules in each panel \textit{p};
  %\textit{P}: Number of panels; 
  \textit{s}: Number of strings;}
\SetKwInOut{Output}{Output}
\Output{Feasibility Result;%\\
        %Conf: Configuration Result;
        }
\For{\textup{each string} $ k (2 \leq k \leq s)$ \textup{and panel} $p$}{$Loss(p,k) = M_{p}(Q_{k}) - M_{p}(Q_{k-1})$}
\For{j = 1 to s}
    {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panes} $< m$}
       {\textup{\textbf{return :}} Feasibility = NO}}
     $PS$ = a set of unselected panels with $M_{p}(Q_{j}) > 0$;\\
     // step 1\\
     sort $PS$ in a lexicographically ascending order of $Loss(p,j+1)$, $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
     // step 2\\
     select panels in the order in $PS$ until $\sum M_{p}(Q_{j})$ for selected panels $\geq m$;\\
     //step 3\\
     group selected panels $LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$ with loss level ($LV_{1}$ is the lowest level);\\
     \For{i = h to 1}
     {find and cancel redundant panels in $LV_{i}$ in the order in $PS$}
     //step 4\\
     \For{i = h to 1}
     {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
    }
    \textup{\textbf{return :}} Feasibility = YES
\end{algorithm}

\subsection{Evaluation}
Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same.

To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays. For each PV array, contains 6 - 24 PV panels connected into 3 - 6 PV strings. For each PV panel, it will has 3 - 8 working current values.

The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}. As shown in Table \ref{result_compare},
% proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.  
from 100 PV arrays, 486 configuration candidates are selected where each candidate is specified with a required current sequence for strings and the number of active modules per string.
Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identify the feasibility of every configuration but that takes a lot of time.
On the other hand, the proposed algorithm rapidly (more than 32,000X faster) checks feasibility while misidentifying only 3 feasible cases. 
% Each PV array has 4 or 5 candidates and our algorithm indeed found PV panel connection for each PV array.

@@

% \begin{table}[ht]
% \caption{PV Cell Parameters}
% \begin{center}
% \begin{tabular}{c|c}
% \hline \hline
% Parameter             & Value  \\ \hline
% Short-Circuit Current & 0.66A  \\
% MPP-Current           & 0.58A  \\
% Open-Circuit Voltage  & 280V   \\
% MPP-Voltage           & 215V  \\
% Max Power Output      & 124.7W 
% \end{tabular}
% \end{center}
% \label{PV_cell_par}
% \end{table}
